---
title: "Project 4: Single Layer Neural Network with L1 Regularization"
author: "Anthony Schroeder"
contributor: "Anthony Schroeder, Junyu Chen, Chadd Frasier, Austin Torrence"
date: "03/08/2019"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Linear Models Report}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}

---
```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

<a id="top"></a>

# Project 3



<a id="intro"></a>
## Introduction


## Linear Regression



## LMSquareLossIterations
This function will take a matrix of training input (n_train x n_features), a vector of labels for the training data vectors (n_train x 1), it will take a scaler value that is the maximum number of iterations in the decent algorithm(scalar > 1), and lastly it will take in a step size which is the size of each step in the gradent descent(scaler > 0). This function will take the matrix of training data and the vector of labels to perform gradient descent on each vector and then create a matrix of weight vectors created from the gradient decent. The function will output th weight matrix by creating a vector for each iteration (n_features+1 x max.iterations). The matrix is larger than the training data so in order to perform matrix multiplication the first element of the weight vectors should be the intercept term. This function will need to minimize the mean loss, not the total loss or eles the gradient decent may not converge. Another method for convergence is to scale the trainign data matrix to a smaller size so the steps of the algorithm will not have to be as large and we will get a much more accurate convergence value. We will compute a scaled input matrix, with a mean of 0 and standard deviation of 1 for each column. This is how we accomplished the matrix normalization.
```{r}
NormalizeMatrix<-function(Matrix)
{
  # ---------- This creates a scaled vector with sd = 1 mean = 0 for each column in matrix-------
  scaled.mat = matrix(nrow = nrow(Matrix),ncol = ncol(Matrix))
  for(col in 1:ncol(Matrix))
  {
    scaled.mat[,col] = (Matrix[,col] - colMeans(Matrix)[col])/sd(Matrix[,col])

  }
  return(as.matrix(scaled.mat))
}
```


**Fromula: ** **$\hat{y} = XW + B$**
Y.hat = data.matrix(TestingData) %*% data.matrix(W.Matrix) +

**Gradient: ** **${W'} = 2X^T(WX-y)^2$**
Gradient = 2*sum(W.Vector*TrainingData + TrainingLabels)*TrainingLabels

**Bias Gradient: ** **${W'} = 2I^T((WX+IB)-y)^2$**
#Gradient = 2*sum(W.Vector*TrainingData + TrainingLabels)*TrainingLabels


#### Linear L2 equations
**We are Looking for : ** **$\hat{W}^{Lambda} = argmin_{W\in R^{P}}$**

**Regularization Gradient: ** **${W'} = 2X^T(X-y)^2 + 2*(Labmda)*W$**




### Logistic equations
#### Logistic Iteration equations

**Gradient: ** **${W'} = 1/(1+e^{-yXW})-y$**

**Cost Function**: 1/n ∑i=1^n L[w^T x_i + b, y_i] + penalty * ||w||_1

#### Linear L2 equations
** We are Looking for : ** **$\hat{W}^{Lambda} = argmin_{W\in R^{P}}$**

** Regularization Gradient: ** **${W'} = 2X^T(X-y)^2 + 2*(Labmda)*W$**


<a id= 'test'></a>
## Testing With Data Sets
we are going to run our code on the following data sets for Binary Classification
- ElemStatLearn::spam 2-class [4601, 57] output is last column (spam).
- ElemStatLearn::SAheart 2-class [462, 9] output is last column (chd).
- ElemStatLearn::zip.train: 10-class [7291, 256] output is first column. (ignore classes other than 0 and 1)
And we will be using the following for regression:
- ElemStatLearn::prostate [97 x 8] output is lpsa column, ignore train column.
- ElemStatLearn::ozone [111 x 3] output is first column (ozone).

```{r, results='hide'}
# Spam Data Set
data(spam, package = "ElemStatLearn")

# SAheart Data Set
data(SAheart, package = "ElemStatLearn")

# zip.train Data Set
data(zip.train, package = "ElemStatLearn")

# prostate Data Set
data(prostate, package = "ElemStatLearn")

# OZone Data Set
data(ozone, package = "ElemStatLearn")
```

# How to use the 'ElemStatLearn' Libraries:

How To use this Linear Models Library:
1. Organize your data into:
  a. Training Data:
  Your data should be a matrix with the Column's containing Feature's, and Row's containing the different training Instances

  b.Training Labels:
  Your data should be a single colomn of numerical values,
    Note: if all labels are (0 or 1)  training will be classified as Binary classification, and be trained accordingly. otherwise, training will be Regressive.

## Testing 
# How to use the 'ElemStatLearn' Libraries:
we are going to run our code on the following data sets.

How To use this Linear Models Library:
1. Organize your data into:
  a. Training Data:
  Your data should be a matrix with the Column's containing Feature's, and Row's containing the different training Instances 
    
  b.Training Labels:
  Your data should be a single colomn of numerical values, 
    Note: if all labels are (0 or 1)  training will be classified as Binary classification, and be trained accordingly. otherwise, training will be Regressive.


- We will include the library(LinearModel), to have access to the given functionality.
- The R script Prep_Libraries.R in the tests/testthat folder contains some simple data manipulation to prep the data to be used for the LinearModel Algorithms.

```{r}
library(LinearModel)
#print(getwd())
source("tests/testthat/Prep_Libraries.R")
source("R/General.R")
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
#source("tests/testthat/LinearModels_Test_Libraries.R")
```

# Binary Classification:
## Data set 1: spam
```{r}
# Data set 1: spam
  Spam<-Prep_Spam()
```
### Code

```{r}
# Data set 1: spam
Spam<-Prep_Spam()
LossMat.fold.n  <- 4
LossMat.fold.vec<-Random_Folds((Spam$n_Elements),LossMat.fold.n)
Data = cbind(Spam$TrainingData ,Spam$TrainingLabels)
#Randomly shuffle the data
#Data<-Data[sample(nrow(Data)),]
SLI.WholeError.Mat = 0
SLI.TrainError.Mat = 0
SLI.TestError.Mat  = 0

ES_CV_Error.WholeError.Mat = 0
ES_CV_Error.TrainError.Mat = 0
ES_CV_Error.TestError.Mat  = 0

SL_L2.WholeError.Mat = 0
SL_L2.TrainError.Mat = 0
SL_L2.TestError.Mat  = 0

SL_L2_Pen.WholeError.Mat = 0
SL_L2_Pen.TrainError.Mat = 0
SL_L2_Pen.TestError.Mat  = 0

SL_L2CV.WholeError.Mat = 0
SL_L2CV.TrainError.Mat = 0
SL_L2CV.TestError.Mat  = 0

#Perform folds.n fold cross validation
for(i in 1:(LossMat.fold.n))
{
  testIndexes <- which(LossMat.fold.vec==i,arr.ind=TRUE)
  testData    <- as.matrix(Data[testIndexes, ])
  trainData   <- as.matrix(Data[-testIndexes, ])

  print("Please wait this might take some time, Iteration:")
  print(i)
  Scalar.Step = 0.1
  Iterations  = 30
  
  #-------------------------LMSquareLossIterations (SLI_Error)--------------
    LMSquareLossIterations.W.Vec <- LMSquareLossIterations(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Iterations,Scalar.Step)
    SLI.WholeError.Vec <-Find_Wmatrix_MeanL2Error(Spam$TrainingData, Spam$TrainingLabels,as.matrix(LMSquareLossIterations.W.Vec),Spam$BinaryClassification)
    #print("dim SLI.WHoleError")
    #print(dim(as.matrix(SLI.WholeError.Vec)))
    #SLI.WholeError.Mat <- cbind(SLI.WholeError.Mat,SLI.WholeError.Vec)
    
    SLI.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(LMSquareLossIterations.W.Vec),Spam$BinaryClassification)
    SLI.TrainError.Mat <- cbind(SLI.TrainError.Mat,SLI.TrainError.Vec)
  
    SLI.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(LMSquareLossIterations.W.Vec),Spam$BinaryClassification)
    SLI.TestError.Mat<- cbind(SLI.TestError.Mat,SLI.TestError.Vec)
  #------------------------------------------------------------------------
  
  #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    ES_CV_Error.fold.n  <- 4
    ES_CV_Error.fold.vec<-Random_Folds(NROW(trainData),ES_CV_Error.fold.n)
    Scalar.Step = 0.1
    Iterations  = 30
    #ES_CV_Error.W.Vec <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Spam$Folds.Vec,Spam$Folds.n,Spam$Iterations)
    ES_CV_Error.List <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ES_CV_Error.fold.vec,ES_CV_Error.fold.n,Iterations)
      
    #ES_CV_Error.WholeError.Vec   <-Find_Wmatrix_MeanL2Error(Spam$TrainingData, Spam$TrainingLabels,as.matrix(ES_CV_Error.List$w.mat),Spam$BinaryClassification)
    #ES_CV_Error.WholeError.Mat <- cbind(ES_CV_Error.WholeError.Mat,ES_CV_Error.WholeError.Vec)
  
    ES_CV_Error.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(ES_CV_Error.List$w.mat),Spam$BinaryClassification)
    #ES_CV_Error.TrainError.Mat <- cbind(ES_CV_Error.TrainError.Mat,ES_CV_Error.TrainError.Vec)
  
    ES_CV_Error.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(ES_CV_Error.List$w.mat),Spam$BinaryClassification)
    #ES_CV_Error.TestError.Mat  <- cbind(ES_CV_Error.TestError.Mat,ES_CV_Error.TestError.Vec)
  #------------------------------------------------------------------------
   
   
   #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    Normalized_TrainingData_List <- NormalizeMatrix_List(trainData[,1:NCOL(trainData)-1])
    Penalty.Scalar = 1
    opt.thresh = .2

    SL_L2.W.Matrix <-LMSquareLossL2(Normalized_TrainingData_List$NormalizedMatrix, trainData[,NCOL(trainData)], Penalty.Scalar, opt.thresh,Spam$Initial.Vector)
    DeNormalized.W.Matrix <-(t(SL_L2.W.Matrix))/Normalized_TrainingData_List$sd

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(Spam$TrainingData, Spam$TrainingLabels,t(DeNormalized.W.Matrix),Spam$BinaryClassification)
    SL_L2.WholeError.Vec <-Find_Wmatrix_MeanL1Error(Spam$TrainingData, Spam$TrainingLabels,t(DeNormalized.W.Matrix),Spam$BinaryClassification)
    SL_L2.WholeError.Mat <- rbind(SL_L2.WholeError.Mat,SL_L2.WholeError.Vec)
    
    SL_L2.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(DeNormalized.W.Matrix),Spam$BinaryClassification)
    SL_L2.TestError.Mat <- rbind(SL_L2.TestError.Mat,SL_L2.TestError.Vec)
    
    SL_L2.TrainError.Vec <-Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(DeNormalized.W.Matrix),Spam$BinaryClassification)
    SL_L2.TrainError.Mat <- rbind(SL_L2.TrainError.Mat,SL_L2.TrainError.Vec)
   #------------------------------------------------------------------------
    
   #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    SL_L2_Pen.W.Mat <-LMSquareLossL2penalties(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)], Spam$Penalty.Vector)

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(Spam$TrainingData, Spam$TrainingLabels,t(DeNormalized.W.Matrix),Spam$BinaryClassification)
    #print("SL_L2_Pen.WholeError.Vec")
    SL_L2_Pen.WholeError.Vec <-Find_Wmatrix_MeanL1Error(Spam$TrainingData, Spam$TrainingLabels,(SL_L2_Pen.W.Mat),Spam$BinaryClassification)
    SL_L2_Pen.WholeError.Mat <- rbind(SL_L2_Pen.WholeError.Mat,SL_L2_Pen.WholeError.Vec)
    
    #print("SL_L2_Pen.TestError.Vec")
    SL_L2_Pen.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],(SL_L2_Pen.W.Mat),Spam$BinaryClassification)
    SL_L2_Pen.TestError.Mat <- rbind(SL_L2_Pen.TestError.Mat,SL_L2_Pen.TestError.Vec)
    
    #print("SL_L2_Pen.TrainError.Vec")
    SL_L2_Pen.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],(SL_L2_Pen.W.Mat),Spam$BinaryClassification)
    SL_L2_Pen.TrainError.Mat <- cbind(SL_L2_Pen.TrainError.Mat,SL_L2_Pen.TrainError.Vec)
   #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    SL_L2CV.fold.n  <- 4
    SL_L2CV.fold.vec<-Random_Folds(NROW(trainData),SL_L2CV.fold.n)
    
    SL_L2CV.List <- LMSquareLossL2CV(as.matrix(trainData[,1:NCOL(trainData)-1]), as.matrix(trainData[,NCOL(trainData)]),as.matrix(t(SL_L2CV.fold.vec)), as.matrix(Spam$Penalty.Vector))
    

    SL_L2CV.WholeError.Vec <- Find_Wmatrix_MeanL1Error(Spam$TrainingData, Spam$TrainingLabels,(SL_L2CV.List$weight.vec),Spam$BinaryClassification)
    SL_L2CV.WholeError.Mat <- rbind(SL_L2CV.WholeError.Mat,SL_L2CV.WholeError.Vec)
    
    
    #SL_L2CV.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(SL_L2CV.W.Mat),Spam$BinaryClassification)
    SL_L2CV.TestError.Vec <- SL_L2CV.List$mean.validation.loss
    SL_L2CV.TestError.Mat <- rbind(SL_L2CV.TestError.Mat,SL_L2CV.TestError.Vec)
    #print("SL_L2CV.TestError.Vec")
    #print(dim(as.matrix(SL_L2CV.TestError.Vec)))
    
    #SL_L2CV.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(SL_L2CV.W.Mat),Spam$BinaryClassification)
    SL_L2CV.TrainError.Vec <- SL_L2CV.List$mean.train.loss.vec
    SL_L2CV.TrainError.Mat <- rbind(SL_L2CV.TrainError.Mat,SL_L2CV.TrainError.Vec)
    #------------------------------------------------------------------------

}
```




### Matrix of loss values
```{r}
#-------------------Matrix of Cross Validation loss values-------------------------------------

#print(SLI.TestError.Mat)

  #Spam_LossMatrix <-rbind(as.double(SLI.TestError.Mat[30,2:5]),ES_CV_Error.TestError.Mat[2,2:5])
  Spam_LossMatrix <-rbind(as.double(SLI.TestError.Mat[30,2:5]),as.double(as.double(t(SL_L2.TestError.Mat[2:5]))))
  Spam_LossMatrix <-rbind(Spam_LossMatrix,as.double(colMeans(SL_L2_Pen.TestError.Mat)[2:5]))
  Spam_LossMatrix <-rbind(Spam_LossMatrix,as.double(SL_L2CV.TrainError.Mat[2:5]))
  print(Spam_LossMatrix)
  

  colnames(Spam_LossMatrix)<-c("Fold1","Fold2","Fold3","Fold4")
  rownames(Spam_LossMatrix)<-c("Linear Squared 30 Iterations","L2 Reg","L2 Reg with Penalty vector","L2 Reg with CV")
  barplot(Spam_LossMatrix, xlab = "Iterations", ylab = "Error",main = "LinearModels_Spam_LossMatrix",legend = (rownames(Spam_LossMatrix)),beside = TRUE)
```





### Train/validation loss plot
```{r}
  #-------------------- Data Set: 1 Spam ----------------------------------
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    plot(rowMeans(as.matrix(SLI.TrainError.Mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "Spam Loss of each matrix",ylim=c(.1,1))
    lines(rowMeans(as.matrix(SLI.TestError.Mat)),type="o", col = "light blue")
    #------------------------------------------------------------------------
    
    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    #lines(rowMeans(as.matrix(ES_CV_Error.TestError.Mat)),type="o", col = "green")
    #lines(rowMeans(as.matrix(ES_CV_Error.TrainError.Mat)),type="o", col = "Light green")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    lines(as.matrix((SL_L2.TestError.Mat[2:NROW(SL_L2.TestError.Mat)])),type="o", col = "black")
    lines(as.matrix(SL_L2.TrainError.Mat[2:NROW(SL_L2.TrainError.Mat)]),type="o", col = "gray")
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    lines(as.matrix((SL_L2_Pen.TestError.Mat[2:NROW(SL_L2_Pen.TestError.Mat)])),type="o", col = "red")
    lines(as.matrix((SL_L2_Pen.TrainError.Mat[2:NROW(SL_L2_Pen.TrainError.Mat)])),type="o", col = "pink")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
  #------------------------------------------------------------------------
```


### Extra Credit attempt: compaire The LinearModels to the KNN
```{r}
  #--------------------NN1ToKmaxPredict------------------------------------
  Spam<-Prep_Spam()
  Fold.vec = Random_Folds(Spam$n_Elements,4)
  Fold.n   = 4
  KNNLearnCV.List = KNNLearnCV(Spam$TrainingData, Spam$TrainingLabels, 30, Fold.vec, Fold.n)
  #------------------------------------------------------------------------

```


```{r}
  plot(colMeans(as.matrix(KNNLearnCV.List$TestMeanError.mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "",ylim=c(0,1))
  lines(colMeans(as.matrix(KNNLearnCV.List$TrainMeanError.mat)),type="o", col = "gray")
  
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
dot.x <- KNNLearnCV.List$selected.KNN
dot.y <- KNNLearnCV.List$TestMeanError.Means[dot.x]

matpoints(x = dot.x,
          y = dot.y,
          col = 2,
          pch = 19)
 # legend(25,30,c("decay","growth"),col=c("blue","red"),pch=c(15,19), y.intersp=1800)
```

## Data set 2: SAheart
```{r}
# Data set 2: SAheart
  SAheart<-Prep_SAheart()
```
### Code 
```{r}
  #-------------------- Data set 2: SAheart ----------------------------------
  LossMat.fold.n  <- 4
  LossMat.fold.vec<-Random_Folds((SAheart$n_Elements),LossMat.fold.n)
  Data = cbind(SAheart$TrainingData ,SAheart$TrainingLabels)
  #Randomly shuffle the data
  #Data<-Data[sample(nrow(Data)),]

  SLI.WholeError.Mat = 0
  SLI.TrainError.Mat = 0
  SLI.TestError.Mat  = 0
  
  ES_CV_Error.WholeError.Mat = 0
  ES_CV_Error.TrainError.Mat = 0
  ES_CV_Error.TestError.Mat  = 0
  
  SL_L2.WholeError.Mat = 0
  SL_L2.TrainError.Mat = 0
  SL_L2.TestError.Mat  = 0
  
  SL_L2_Pen.WholeError.Mat = 0
  SL_L2_Pen.TrainError.Mat = 0
  SL_L2_Pen.TestError.Mat  = 0
  
  SL_L2CV.WholeError.Mat = 0
  SL_L2CV.TrainError.Mat = 0
  SL_L2CV.TestError.Mat  = 0
  #Perform folds.n fold cross validation
  for(i in 1:(LossMat.fold.n))
  {
    testIndexes <- which(LossMat.fold.vec==i,arr.ind=TRUE)
    testData    <- as.matrix(Data[testIndexes, ])
    trainData   <- as.matrix(Data[-testIndexes, ])
  
    print("Please wait this might take some time, Iteration:")
    print(i)
    
    Scalar.Step = 0.01
    Iterations  = 30
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    LMSquareLossIterations.W.Vec <- LMSquareLossIterations(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Iterations,Scalar.Step)
    SLI.WholeError.Vec <-Find_Wmatrix_MeanL2Error(SAheart$TrainingData, SAheart$TrainingLabels,as.matrix(LMSquareLossIterations.W.Vec),SAheart$BinaryClassification)
    #print("dim SLI.WHoleError")
    #print(dim(as.matrix(SLI.WholeError.Vec)))
    SLI.WholeError.Mat <- cbind(SLI.WholeError.Mat,SLI.WholeError.Vec)

   SLI.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(LMSquareLossIterations.W.Vec),SAheart$BinaryClassification)
   SLI.TrainError.Mat <- cbind(SLI.TrainError.Mat,SLI.TrainError.Vec)

    SLI.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(LMSquareLossIterations.W.Vec),SAheart$BinaryClassification)
    SLI.TestError.Mat<- cbind(SLI.TestError.Mat,SLI.TestError.Vec)
    #------------------------------------------------------------------------

    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    ES_CV_Error.fold.n  <- 4
    ES_CV_Error.fold.vec<-Random_Folds(NROW(trainData),ES_CV_Error.fold.n)

    #ES_CV_Error.W.Vec <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],SAheart$Folds.Vec,SAheart$Folds.n,SAheart$Iterations)
    ES_CV_Error.List <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ES_CV_Error.fold.vec,ES_CV_Error.fold.n,Iterations)
    
    ES_CV_Error.WholeError.Vec   <-Find_Wmatrix_MeanL2Error(SAheart$TrainingData, SAheart$TrainingLabels,as.matrix(ES_CV_Error.List$w.mat),SAheart$BinaryClassification)
    #print("dim ES_CV_Error.WholeError.Vec")
    #print(dim(as.matrix(ES_CV_Error.WholeError.Vec)))
    #ES_CV_Error.WholeError.Mat <- cbind(ES_CV_Error.WholeError.Mat,ES_CV_Error.WholeError.Vec)

    ES_CV_Error.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(ES_CV_Error.List$w.mat),SAheart$BinaryClassification)
    #ES_CV_Error.TrainError.Mat <- cbind(ES_CV_Error.TrainError.Mat,ES_CV_Error.TrainError.Vec)

    ES_CV_Error.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(ES_CV_Error.List$w.mat),SAheart$BinaryClassification)
    #ES_CV_Error.TestError.Mat  <- cbind(ES_CV_Error.TestError.Mat,ES_CV_Error.TestError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    Normalized_TrainingData_List <- NormalizeMatrix_List(trainData[,1:NCOL(trainData)-1])
    Penalty.Scalar = 1
    opt.thresh = .2

    SL_L2.W.Matrix <-LMSquareLossL2(Normalized_TrainingData_List$NormalizedMatrix, trainData[,NCOL(trainData)], Penalty.Scalar, opt.thresh,SAheart$Initial.Vector)
    DeNormalized.W.Matrix <-(t(SL_L2.W.Matrix))/Normalized_TrainingData_List$sd

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(SAheart$TrainingData, SAheart$TrainingLabels,t(DeNormalized.W.Matrix),SAheart$BinaryClassification)
    SL_L2.WholeError.Vec <-Find_Wmatrix_MeanL1Error(SAheart$TrainingData, SAheart$TrainingLabels,t(DeNormalized.W.Matrix),SAheart$BinaryClassification)
    SL_L2.WholeError.Mat <- rbind(SL_L2.WholeError.Mat,SL_L2.WholeError.Vec)
    
    SL_L2.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(DeNormalized.W.Matrix),SAheart$BinaryClassification)
    SL_L2.TestError.Mat <- rbind(SL_L2.TestError.Mat,SL_L2.TestError.Vec)
    
    SL_L2.TrainError.Vec <-Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(DeNormalized.W.Matrix),SAheart$BinaryClassification)
    SL_L2.TrainError.Mat <- rbind(SL_L2.TrainError.Mat,SL_L2.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    Penalty.Scalar = 1
    opt.thresh = .2
    SL_L2_Pen.W.Mat <-LMSquareLossL2penalties(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)], SAheart$Penalty.Vector)

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(SAheart$TrainingData, SAheart$TrainingLabels,t(DeNormalized.W.Matrix),SAheart$BinaryClassification)
    #print("SL_L2_Pen.WholeError.Vec")
    SL_L2_Pen.WholeError.Vec <-Find_Wmatrix_MeanL1Error(SAheart$TrainingData, SAheart$TrainingLabels,(SL_L2_Pen.W.Mat),SAheart$BinaryClassification)
    SL_L2_Pen.WholeError.Mat <- rbind(SL_L2_Pen.WholeError.Mat,SL_L2_Pen.WholeError.Vec)
    
    #print("SL_L2_Pen.TestError.Vec")
    SL_L2_Pen.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],(SL_L2_Pen.W.Mat),SAheart$BinaryClassification)
    SL_L2_Pen.TestError.Mat <- rbind(SL_L2_Pen.TestError.Mat,SL_L2_Pen.TestError.Vec)
    
    #print("SL_L2_Pen.TrainError.Vec")
    SL_L2_Pen.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],(SL_L2_Pen.W.Mat),SAheart$BinaryClassification)
    SL_L2_Pen.TrainError.Mat <- rbind(SL_L2_Pen.TrainError.Mat,SL_L2_Pen.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    SL_L2CV.fold.n  <- 2
    SL_L2CV.fold.vec<-Random_Folds(NROW(trainData),SL_L2CV.fold.n)
      
    SL_L2CV.List <- LMSquareLossL2CV(as.matrix(trainData[,1:NCOL(trainData)-1]), as.matrix(trainData[,NCOL(trainData)]),as.matrix(t(SL_L2CV.fold.vec)), as.matrix(SAheart$Penalty.Vector))
      

    SL_L2CV.WholeError.Vec <- Find_Wmatrix_MeanL1Error(SAheart$TrainingData, SAheart$TrainingLabels,(SL_L2CV.List$weight.vec),SAheart$BinaryClassification)
    SL_L2CV.WholeError.Mat <- rbind(SL_L2CV.WholeError.Mat,SL_L2CV.WholeError.Vec)
      
      
    #SL_L2CV.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(SL_L2CV.W.Mat),SAheart$BinaryClassification)
    SL_L2CV.TestError.Vec <- SL_L2CV.List$mean.validation.loss
    SL_L2CV.TestError.Mat <- rbind(SL_L2CV.TestError.Mat,SL_L2CV.TestError.Vec)
    #print("SL_L2CV.TestError.Vec")
    #print(dim(as.matrix(SL_L2CV.TestError.Vec)))
      
    #SL_L2CV.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(SL_L2CV.W.Mat),SAheart$BinaryClassification)
    SL_L2CV.TrainError.Vec <- SL_L2CV.List$mean.train.loss.vec
    SL_L2CV.TrainError.Mat <- rbind(SL_L2CV.TrainError.Mat,SL_L2CV.TrainError.Vec)
    #print("SL_L2CV.TrainError.Vec")
    #print(dim(as.matrix(SL_L2CV.TrainError.Vec)))
    #------------------------------------------------------------------------
  }

  #------------------------------------------------------------------------
```
### Matrix of loss values
```{r}
#-------------------Matrix of Cross Validation loss values-------------------------------------

#print(SLI.TestError.Mat)

  #Spam_LossMatrix <-rbind(,ES_CV_Error.TestError.Mat[2,2:5])
  Spam_LossMatrix <-rbind(as.double(SLI.TestError.Mat[30,2:5]),as.double(as.double(t(SL_L2.TestError.Mat[2:5]))))
  Spam_LossMatrix <-rbind(Spam_LossMatrix,as.double(colMeans(SL_L2_Pen.TestError.Mat)[2:5]))
  Spam_LossMatrix <-rbind(Spam_LossMatrix,as.double(SL_L2CV.TrainError.Mat[2:5]))
  print(Spam_LossMatrix)
  

  colnames(Spam_LossMatrix)<-c("Fold1","Fold2","Fold3","Fold4")
  rownames(Spam_LossMatrix)<-c("Linear Squared 30 Iterations","L2 Reg","L2 Reg with Penalty vector","L2 Reg with CV")
  barplot(Spam_LossMatrix, xlab = "Iterations", ylab = "Error",main = "SAheart_LossMatrix",legend = (rownames(Spam_LossMatrix)),beside = TRUE)
```

### Train/validation loss plot


```{r}
  #-------------------- Graph Data Set: 2 SAheart -----------------------------
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    plot(rowMeans(as.matrix(SLI.TrainError.Mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "SAheart Loss of each matrix",ylim=c(.1,1))
    lines(rowMeans(as.matrix(SLI.TestError.Mat)),type="o", col = "light blue")
    #------------------------------------------------------------------------
    
    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    lines(rowMeans(as.matrix(ES_CV_Error.TestError.Vec)),type="o", col = "green")
    lines(rowMeans(as.matrix(ES_CV_Error.TrainError.Vec)),type="o", col = "Light green")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    lines(as.matrix((SL_L2.TestError.Mat[2:NROW(SL_L2.TestError.Mat)])),type="o", col = "black")
    lines(as.matrix(SL_L2.TrainError.Mat[2:NROW(SL_L2.TrainError.Mat)]),type="o", col = "gray")
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    lines(as.matrix((SL_L2_Pen.TestError.Mat[2:NROW(SL_L2_Pen.TestError.Mat)])),type="o", col = "red")
    lines(as.matrix((SL_L2_Pen.TrainError.Mat[2:NROW(SL_L2_Pen.TrainError.Mat)])),type="o", col = "pink")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
  #------------------------------------------------------------------------
```
### Extra Credit attempt: compaire The LinearModels to the KNN
```{r}
  #--------------------NN1ToKmaxPredict------------------------------------
  SAheart<-Prep_SAheart()
  Fold.vec = Random_Folds(SAheart$n_Elements,4)
  Fold.n   = 4
  KNNLearnCV.List = KNNLearnCV(SAheart$TrainingData, SAheart$TrainingLabels, 30, Fold.vec, Fold.n)

  barplot(KNNLearnCV.List$TestMeanError.Means,main = "SAheart: KNNLearnCV L2 Mean Error",xlab = "KNN Compared",ylab = "Error",beside = TRUE)
  #------------------------------------------------------------------------

```
```{r}
  plot(colMeans(as.matrix(KNNLearnCV.List$TestMeanError.mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "",ylim=c(0,1))
  lines(colMeans(as.matrix(KNNLearnCV.List$TrainMeanError.mat)),type="o", col = "gray")
  
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
dot.x <- KNNLearnCV.List$selected.KNN
dot.y <- KNNLearnCV.List$TestMeanError.Means[dot.x]

matpoints(x = dot.x,
          y = dot.y,
          col = 2,
          pch = 19)
 # legend(25,30,c("decay","growth"),col=c("blue","red"),pch=c(15,19), y.intersp=1800)
```


## Data set 3: Zip.train
```{r}
  ZipTrain<-Prep_ZipTrain()
```
### Code 
```{r}
  #-------------------- Data set 3: Zip.train ----------------------------------
  LossMat.fold.n  <- 4
  LossMat.fold.vec<-Random_Folds((ZipTrain$n_Elements),LossMat.fold.n)
  Data = cbind(ZipTrain$TrainingData ,ZipTrain$TrainingLabels)
  #Randomly shuffle the data
  #Data<-Data[sample(nrow(Data)),]

  SLI.WholeError.Mat = 0
  SLI.TrainError.Mat = 0
  SLI.TestError.Mat  = 0
  
  ES_CV_Error.WholeError.Mat = 0
  ES_CV_Error.TrainError.Mat = 0
  ES_CV_Error.TestError.Mat  = 0
  
  SL_L2.WholeError.Mat = 0
  SL_L2.TrainError.Mat = 0
  SL_L2.TestError.Mat  = 0
  
  SL_L2_Pen.WholeError.Mat = 0
  SL_L2_Pen.TrainError.Mat = 0
  SL_L2_Pen.TestError.Mat  = 0
  
  SL_L2CV.WholeError.Mat = 0
  SL_L2CV.TrainError.Mat = 0
  SL_L2CV.TestError.Mat  = 0
  #Perform folds.n fold cross validation
  for(i in 1:(LossMat.fold.n))
  {
    testIndexes <- which(LossMat.fold.vec==i,arr.ind=TRUE)
    testData    <- as.matrix(Data[testIndexes, ])
    trainData   <- as.matrix(Data[-testIndexes, ])
  
    print("Please wait this might take some time, Iteration:")
    print(i)
    
    Scalar.Step = 0.01
    Iterations  = 30
    
    #-------------------------LMSquareLossIterations (SLI_Error)-------------
    LMSquareLossIterations.W.Vec <- LMSquareLossIterations(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Iterations,Scalar.Step)
    SLI.WholeError.Vec <-Find_Wmatrix_MeanL2Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,as.matrix(LMSquareLossIterations.W.Vec),ZipTrain$BinaryClassification)
    print("dim SLI.WHoleError")
    print(dim(as.matrix(SLI.WholeError.Vec)))
    SLI.WholeError.Mat <- cbind(SLI.WholeError.Mat,SLI.WholeError.Vec)

    SLI.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(LMSquareLossIterations.W.Vec),ZipTrain$BinaryClassification)
    SLI.TrainError.Mat <- cbind(SLI.TrainError.Mat,SLI.TrainError.Vec)

    SLI.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(LMSquareLossIterations.W.Vec),ZipTrain$BinaryClassification)
   SLI.TestError.Mat<- cbind(SLI.TestError.Mat,SLI.TestError.Vec)
    #------------------------------------------------------------------------

    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    ES_CV_Error.fold.n  <- 4
    ES_CV_Error.fold.vec<-Random_Folds(NROW(trainData),ES_CV_Error.fold.n)

    #ES_CV_Error.W.Vec <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ZipTrain$Folds.Vec,ZipTrain$Folds.n,ZipTrain$Iterations)
    ES_CV_Error.List <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ES_CV_Error.fold.vec,ES_CV_Error.fold.n,Iterations)
    
    ES_CV_Error.WholeError.Vec   <-Find_Wmatrix_MeanL2Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,as.matrix(ES_CV_Error.List$w.mat),ZipTrain$BinaryClassification)
    #print("dim ES_CV_Error.WholeError.Vec")
    #print(dim(as.matrix(ES_CV_Error.WholeError.Vec)))
    #ES_CV_Error.WholeError.Mat <- cbind(ES_CV_Error.WholeError.Mat,ES_CV_Error.WholeError.Vec)

    ES_CV_Error.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(ES_CV_Error.List$w.mat),ZipTrain$BinaryClassification)
    #ES_CV_Error.TrainError.Mat <- cbind(ES_CV_Error.TrainError.Mat,ES_CV_Error.TrainError.Vec)

    ES_CV_Error.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(ES_CV_Error.List$w.mat),ZipTrain$BinaryClassification)
    #ES_CV_Error.TestError.Mat  <- cbind(ES_CV_Error.TestError.Mat,ES_CV_Error.TestError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    Normalized_TrainingData_List <- NormalizeMatrix_List(trainData[,1:NCOL(trainData)-1])
    Penalty.Scalar = 1
    opt.thresh = .2

    SL_L2.W.Matrix <-LMSquareLossL2(Normalized_TrainingData_List$NormalizedMatrix, trainData[,NCOL(trainData)], Penalty.Scalar, opt.thresh,ZipTrain$Initial.Vector)
    DeNormalized.W.Matrix <-(t(SL_L2.W.Matrix))/Normalized_TrainingData_List$sd

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,t(DeNormalized.W.Matrix),ZipTrain$BinaryClassification)
    SL_L2.WholeError.Vec <-Find_Wmatrix_MeanL1Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,t(DeNormalized.W.Matrix),ZipTrain$BinaryClassification)
    SL_L2.WholeError.Mat <- rbind(SL_L2.WholeError.Mat,SL_L2.WholeError.Vec)
    
    SL_L2.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(DeNormalized.W.Matrix),ZipTrain$BinaryClassification)
    SL_L2.TestError.Mat <- rbind(SL_L2.TestError.Mat,SL_L2.TestError.Vec)
    
    SL_L2.TrainError.Vec <-Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(DeNormalized.W.Matrix),ZipTrain$BinaryClassification)
    SL_L2.TrainError.Mat <- rbind(SL_L2.TrainError.Mat,SL_L2.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    Penalty.Scalar = 1
    opt.thresh = .2
    SL_L2_Pen.W.Mat <-LMSquareLossL2penalties(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)], ZipTrain$Penalty.Vector)

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,t(DeNormalized.W.Matrix),ZipTrain$BinaryClassification)
    #print("SL_L2_Pen.WholeError.Vec")
    SL_L2_Pen.WholeError.Vec <-Find_Wmatrix_MeanL1Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,(SL_L2_Pen.W.Mat),ZipTrain$BinaryClassification)
    SL_L2_Pen.WholeError.Mat <- rbind(SL_L2_Pen.WholeError.Mat,SL_L2_Pen.WholeError.Vec)
    
    #print("SL_L2_Pen.TestError.Vec")
    SL_L2_Pen.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],(SL_L2_Pen.W.Mat),ZipTrain$BinaryClassification)
    SL_L2_Pen.TestError.Mat <- rbind(SL_L2_Pen.TestError.Mat,SL_L2_Pen.TestError.Vec)
    
    #print("SL_L2_Pen.TrainError.Vec")
    SL_L2_Pen.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],(SL_L2_Pen.W.Mat),ZipTrain$BinaryClassification)
    SL_L2_Pen.TrainError.Mat <- rbind(SL_L2_Pen.TrainError.Mat,SL_L2_Pen.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
      SL_L2CV.fold.n  <- 4
      SL_L2CV.fold.vec<-Random_Folds(NROW(trainData),SL_L2CV.fold.n)
      
      SL_L2CV.List <- LMSquareLossL2CV(as.matrix(trainData[,1:NCOL(trainData)-1]), as.matrix(trainData[,NCOL(trainData)]),as.matrix(t(SL_L2CV.fold.vec)), as.matrix(ZipTrain$Penalty.Vector))
      

      SL_L2CV.WholeError.Vec <- Find_Wmatrix_MeanL1Error(ZipTrain$TrainingData, ZipTrain$TrainingLabels,(SL_L2CV.List$weight.vec),ZipTrain$BinaryClassification)
      SL_L2CV.WholeError.Mat <- rbind(SL_L2CV.WholeError.Mat,SL_L2CV.WholeError.Vec)
      
      
      #SL_L2CV.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(SL_L2CV.W.Mat),ZipTrain$BinaryClassification)
      SL_L2CV.TestError.Vec <- SL_L2CV.List$mean.validation.loss
      SL_L2CV.TestError.Mat <- rbind(SL_L2CV.TestError.Mat,SL_L2CV.TestError.Vec)
      #print("SL_L2CV.TestError.Vec")
      #print(dim(as.matrix(SL_L2CV.TestError.Vec)))
      
      #SL_L2CV.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(SL_L2CV.W.Mat),ZipTrain$BinaryClassification)
      SL_L2CV.TrainError.Vec <- SL_L2CV.List$mean.train.loss.vec
      SL_L2CV.TrainError.Mat <- rbind(SL_L2CV.TrainError.Mat,SL_L2CV.TrainError.Vec)
      #print("SL_L2CV.TrainError.Vec")
      #print(dim(as.matrix(SL_L2CV.TrainError.Vec)))
    #------------------------------------------------------------------------
  }


  #------------------------------------------------------------------------
```
### Matrix of loss values
```{r}
#-------------------Matrix of Cross Validation loss values-------------------------------------

#print(SLI.TestError.Mat)

  #ZipTrain_LossMatrix <-rbind(,ES_CV_Error.TestError.Mat[2,2:5])
  ZipTrain_LossMatrix <-rbind(as.double(SLI.TestError.Mat[30,2:5]),as.double(as.double(t(SL_L2.TestError.Mat[2:5]))))
  ZipTrain_LossMatrix <-rbind(ZipTrain_LossMatrix,as.double(colMeans(SL_L2_Pen.TestError.Mat)[2:5]))
  ZipTrain_LossMatrix <-rbind(ZipTrain_LossMatrix,as.double(SL_L2CV.TrainError.Mat[2:5]))

  

  colnames(ZipTrain_LossMatrix)<-c("Fold1","Fold2","Fold3","Fold4")
  rownames(ZipTrain_LossMatrix)<-c("Linear Squared 30 Iterations","L2 Reg","L2 Reg with Penalty vector","L2 Reg with CV")
  barplot(ZipTrain_LossMatrix, xlab = "Iterations", ylab = "Error",main = "_LossMatrix",legend = (rownames(Spam_LossMatrix)),beside = TRUE)
```

### Train/validation loss plot
```{r}
  #-------------------- Graph Data Set: 2 SAheart -----------------------------
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    plot(rowMeans(as.matrix(SLI.TrainError.Mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "SAheart Loss of each matrix",ylim=c(0,200))
    lines(rowMeans(as.matrix(SLI.TestError.Mat)),type="o", col = "light blue")
    #------------------------------------------------------------------------
    
    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    lines(rowMeans(as.matrix(ES_CV_Error.TestError.Vec)),type="o", col = "green")
    lines(rowMeans(as.matrix(ES_CV_Error.TrainError.Vec)),type="o", col = "Light green")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    lines(as.matrix((SL_L2.TestError.Mat[2:NROW(SL_L2.TestError.Mat)])),type="o", col = "black")
    lines(as.matrix(SL_L2.TrainError.Mat[2:NROW(SL_L2.TrainError.Mat)]),type="o", col = "gray")
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    
    lines(as.matrix((SL_L2_Pen.TrainError.Mat[2:NROW(SL_L2_Pen.TrainError.Mat)])),type="o", col = "pink")
    lines(as.matrix((SL_L2_Pen.TestError.Mat[2:NROW(SL_L2_Pen.TestError.Mat)])),type="o", col = "red")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
  #------------------------------------------------------------------------
```
### Extra Credit attempt: compaire The LinearModels to the KNN
```{r}
  #--------------------KNNLearnCV------------------------------------
  Ziptrain<-Prep_ZipTrain()
  Fold.vec = Random_Folds(Ziptrain$n_Elements,4)
  Fold.n   = 4
  KNNLearnCV.List = KNNLearnCV(Ziptrain$TrainingData, Ziptrain$TrainingLabels, 30, Fold.vec, Fold.n)

  barplot(KNNLearnCV.List$TestMeanError.Means,main = "Ziptrain: KNNLearnCV L2 Mean Error",xlab = "KNN Compared",ylab = "Error",beside = TRUE)
  #------------------------------------------------------------------------

```



## Data set 4: Prostate
```{r}
   Prostate<-Prep_Prostate()
```
### Code 
```{r}
  #-------------------- Data set 4: Prostate ----------------------------------
  LossMat.fold.n  <- 4
  LossMat.fold.vec<-Random_Folds((Prostate$n_Elements),LossMat.fold.n)
  Data = cbind(Prostate$TrainingData ,Prostate$TrainingLabels)
  #Randomly shuffle the data
  #Data<-Data[sample(nrow(Data)),]

  SLI.WholeError.Mat = 0
  SLI.TrainError.Mat = 0
  SLI.TestError.Mat  = 0
  
  ES_CV_Error.WholeError.Mat = 0
  ES_CV_Error.TrainError.Mat = 0
  ES_CV_Error.TestError.Mat  = 0
  
  SL_L2.WholeError.Mat = 0
  SL_L2.TrainError.Mat = 0
  SL_L2.TestError.Mat  = 0
  
  SL_L2_Pen.WholeError.Mat = 0
  SL_L2_Pen.TrainError.Mat = 0
  SL_L2_Pen.TestError.Mat  = 0
  
  SL_L2CV.WholeError.Mat = 0
  SL_L2CV.TrainError.Mat = 0
  SL_L2CV.TestError.Mat  = 0
  #Perform folds.n fold cross validation
  for(i in 1:(LossMat.fold.n))
  {
    testIndexes <- which(LossMat.fold.vec==i,arr.ind=TRUE)
    testData    <- as.matrix(Data[testIndexes, ])
    trainData   <- as.matrix(Data[-testIndexes, ])
  
    print("Please wait this might take some time, Iteration:")
    print(i)
    
    Scalar.Step = 0.1
    Iterations  = 30

    #-------------------------LMSquareLossIterations (SLI_Error)-------------

    LMSquareLossIterations.W.Vec <- LMSquareLossIterations(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Iterations,Scalar.Step)
    SLI.WholeError.Vec <-Find_Wmatrix_MeanL2Error(Prostate$TrainingData, Prostate$TrainingLabels,as.matrix(LMSquareLossIterations.W.Vec),Prostate$BinaryClassification)
    print("dim SLI.WHoleError")
    print(dim(as.matrix(SLI.WholeError.Vec)))
    SLI.WholeError.Mat <- cbind(SLI.WholeError.Mat,SLI.WholeError.Vec)

    SLI.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(LMSquareLossIterations.W.Vec),Prostate$BinaryClassification)
    SLI.TrainError.Mat <- cbind(SLI.TrainError.Mat,SLI.TrainError.Vec)

    SLI.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(LMSquareLossIterations.W.Vec),Prostate$BinaryClassification)
    SLI.TestError.Mat<- cbind(SLI.TestError.Mat,SLI.TestError.Vec)
    #------------------------------------------------------------------------

    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    ES_CV_Error.fold.n  <- 4
    ES_CV_Error.fold.vec<-Random_Folds(NROW(trainData),ES_CV_Error.fold.n)
    Scalar.Step = 0.1
    Iterations  = 30
    #ES_CV_Error.W.Vec <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Prostate$Folds.Vec,Prostate$Folds.n,Prostate$Iterations)
    ES_CV_Error.List <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ES_CV_Error.fold.vec,ES_CV_Error.fold.n,Iterations)
    
    ES_CV_Error.WholeError.Vec   <-Find_Wmatrix_MeanL2Error(Prostate$TrainingData, Prostate$TrainingLabels,as.matrix(ES_CV_Error.List$w.mat),Prostate$BinaryClassification)
    #print("dim ES_CV_Error.WholeError.Vec")
    #print(dim(as.matrix(ES_CV_Error.WholeError.Vec)))
    #ES_CV_Error.WholeError.Mat <- cbind(ES_CV_Error.WholeError.Mat,ES_CV_Error.WholeError.Vec)

   ES_CV_Error.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(ES_CV_Error.List$w.mat),Prostate$BinaryClassification)
   #ES_CV_Error.TrainError.Mat <- cbind(ES_CV_Error.TrainError.Mat,ES_CV_Error.TrainError.Vec)

   ES_CV_Error.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(ES_CV_Error.List$w.mat),Prostate$BinaryClassification)
   #ES_CV_Error.TestError.Mat  <- cbind(ES_CV_Error.TestError.Mat,ES_CV_Error.TestError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    Normalized_TrainingData_List <- NormalizeMatrix_List(trainData[,1:NCOL(trainData)-1])
    Penalty.Scalar = 1
    opt.thresh = .2

    SL_L2.W.Matrix <-LMSquareLossL2(Normalized_TrainingData_List$NormalizedMatrix, trainData[,NCOL(trainData)], Penalty.Scalar, opt.thresh,Prostate$Initial.Vector)
    DeNormalized.W.Matrix <-(t(SL_L2.W.Matrix))/Normalized_TrainingData_List$sd

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(Prostate$TrainingData, Prostate$TrainingLabels,t(DeNormalized.W.Matrix),Prostate$BinaryClassification)
    SL_L2.WholeError.Vec <-Find_Wmatrix_MeanL1Error(Prostate$TrainingData, Prostate$TrainingLabels,t(DeNormalized.W.Matrix),Prostate$BinaryClassification)
    SL_L2.WholeError.Mat <- rbind(SL_L2.WholeError.Mat,SL_L2.WholeError.Vec)
    
    SL_L2.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(DeNormalized.W.Matrix),Prostate$BinaryClassification)
    SL_L2.TestError.Mat <- rbind(SL_L2.TestError.Mat,SL_L2.TestError.Vec)
    
    SL_L2.TrainError.Vec <-Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(DeNormalized.W.Matrix),Prostate$BinaryClassification)
    SL_L2.TrainError.Mat <- rbind(SL_L2.TrainError.Mat,SL_L2.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    Penalty.Scalar = 1
    opt.thresh = .2
    SL_L2_Pen.W.Mat <-LMSquareLossL2penalties(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)], Prostate$Penalty.Vector)

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(Prostate$TrainingData, Prostate$TrainingLabels,t(DeNormalized.W.Matrix),Prostate$BinaryClassification)
    #print("SL_L2_Pen.WholeError.Vec")
    SL_L2_Pen.WholeError.Vec <-Find_Wmatrix_MeanL1Error(Prostate$TrainingData, Prostate$TrainingLabels,(SL_L2_Pen.W.Mat),Prostate$BinaryClassification)
    SL_L2_Pen.WholeError.Mat <- rbind(SL_L2_Pen.WholeError.Mat,SL_L2_Pen.WholeError.Vec)
    
    #print("SL_L2_Pen.TestError.Vec")
    SL_L2_Pen.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],(SL_L2_Pen.W.Mat),Prostate$BinaryClassification)
    SL_L2_Pen.TestError.Mat <- rbind(SL_L2_Pen.TestError.Mat,SL_L2_Pen.TestError.Vec)
    
    #print("SL_L2_Pen.TrainError.Vec")
    SL_L2_Pen.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],(SL_L2_Pen.W.Mat),Prostate$BinaryClassification)
    SL_L2_Pen.TrainError.Mat <- rbind(SL_L2_Pen.TrainError.Mat,SL_L2_Pen.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
      SL_L2CV.fold.n  <- 4
      SL_L2CV.fold.vec<-Random_Folds(NROW(trainData),SL_L2CV.fold.n)
      
      SL_L2CV.List <- LMSquareLossL2CV(as.matrix(trainData[,1:NCOL(trainData)-1]), as.matrix(trainData[,NCOL(trainData)]),as.matrix(t(SL_L2CV.fold.vec)), as.matrix(Prostate$Penalty.Vector))
      

      SL_L2CV.WholeError.Vec <- Find_Wmatrix_MeanL1Error(Prostate$TrainingData, Prostate$TrainingLabels,(SL_L2CV.List$weight.vec),Prostate$BinaryClassification)
      SL_L2CV.WholeError.Mat <- rbind(SL_L2CV.WholeError.Mat,SL_L2CV.WholeError.Vec)
      
      
      #SL_L2CV.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(SL_L2CV.W.Mat),Prostate$BinaryClassification)
      SL_L2CV.TestError.Vec <- SL_L2CV.List$mean.validation.loss
      SL_L2CV.TestError.Mat <- rbind(SL_L2CV.TestError.Mat,SL_L2CV.TestError.Vec)
      #print("SL_L2CV.TestError.Vec")
      #print(dim(as.matrix(SL_L2CV.TestError.Vec)))
      
      #SL_L2CV.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(SL_L2CV.W.Mat),Prostate$BinaryClassification)
      SL_L2CV.TrainError.Vec <- SL_L2CV.List$mean.train.loss.vec
      SL_L2CV.TrainError.Mat <- rbind(SL_L2CV.TrainError.Mat,SL_L2CV.TrainError.Vec)
      #print("SL_L2CV.TrainError.Vec")
      #print(dim(as.matrix(SL_L2CV.TrainError.Vec)))
      
    #------------------------------------------------------------------------
  }

  #------------------------------------------------------------------------
```
### Matrix of loss values
```{r}
#-------------------Matrix of Cross Validation loss values-------------------------------------


```
### Train/validation loss plot
```{r}
  #-------------------- Data set 4: Prostate -----------------------------
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    plot(rowMeans(as.matrix(SLI.TrainError.Mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "SAheart Loss of each matrix")
    lines(rowMeans(as.matrix(SLI.TestError.Mat)),type="o", col = "light blue")
    #------------------------------------------------------------------------
    
    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    lines(rowMeans(as.matrix(ES_CV_Error.TestError.Vec)),type="o", col = "green")
    lines(rowMeans(as.matrix(ES_CV_Error.TrainError.Vec)),type="o", col = "Light green")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    lines(as.matrix((SL_L2.TestError.Mat[2:NROW(SL_L2.TestError.Mat)])),type="o", col = "black")
    lines(as.matrix(SL_L2.TrainError.Mat[2:NROW(SL_L2.TrainError.Mat)]),type="o", col = "gray")
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    lines(as.matrix((SL_L2_Pen.TestError.Mat[2:NROW(SL_L2_Pen.TestError.Mat)])),type="o", col = "red")
    lines(as.matrix((SL_L2_Pen.TrainError.Mat[2:NROW(SL_L2_Pen.TrainError.Mat)])),type="o", col = "pink")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
  #------------------------------------------------------------------------
```
### Extra Credit attempt: compaire The LinearModels to the KNN
```{r}
  #--------------------NN1ToKmaxPredict------------------------------------
  Prostate<-Prep_Prostate()
  Fold.vec = Random_Folds(Prostate$n_Elements,4)
  Fold.n   = 4
  KNNLearnCV.List = KNNLearnCV(Prostate$TrainingData, Prostate$TrainingLabels, 30, Fold.vec, Fold.n)

  barplot(KNNLearnCV.List$TestMeanError.Means,main = "Prostate: KNNLearnCV L2 Mean Error",xlab = "KNN Compared",ylab = "Error",beside = TRUE)
  #------------------------------------------------------------------------
```



## Data set 5: Ozone
```{r}
  OZone<-Prep_Ozone()
```
### Code 
```{r}
  #-------------------- Data set 5: Ozone ----------------------------------
  LossMat.fold.n  <- 4
  LossMat.fold.vec<-Random_Folds((OZone$n_Elements),LossMat.fold.n)
  Data = cbind(OZone$TrainingData ,OZone$TrainingLabels)
  #Randomly shuffle the data
  #Data<-Data[sample(nrow(Data)),]

  SLI.WholeError.Mat = 0
  SLI.TrainError.Mat = 0
  SLI.TestError.Mat  = 0
  
  ES_CV_Error.WholeError.Mat = 0
  ES_CV_Error.TrainError.Mat = 0
  ES_CV_Error.TestError.Mat  = 0
  
  SL_L2.WholeError.Mat = 0
  SL_L2.TrainError.Mat = 0
  SL_L2.TestError.Mat  = 0
  
  SL_L2_Pen.WholeError.Mat = 0
  SL_L2_Pen.TrainError.Mat = 0
  SL_L2_Pen.TestError.Mat  = 0
  
  SL_L2CV.WholeError.Mat = 0
  SL_L2CV.TrainError.Mat = 0
  SL_L2CV.TestError.Mat  = 0
  #Perform folds.n fold cross validation
  for(i in 1:(LossMat.fold.n))
  {
    testIndexes <- which(LossMat.fold.vec==i,arr.ind=TRUE)
    testData    <- as.matrix(Data[testIndexes, ])
    trainData   <- as.matrix(Data[-testIndexes, ])
  
    print("Please wait this might take some time, Iteration:")
    print(i)
    

    #-------------------------LMSquareLossIterations (SLI_Error)-------------
    Scalar.Step = 0.1
    Iterations  = 30
    LMSquareLossIterations.W.Vec <- LMSquareLossIterations(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],Iterations,Scalar.Step)
    SLI.WholeError.Vec <-Find_Wmatrix_MeanL2Error(OZone$TrainingData, OZone$TrainingLabels,as.matrix(LMSquareLossIterations.W.Vec),OZone$BinaryClassification)
    print("dim SLI.WHoleError")
    print(dim(as.matrix(SLI.WholeError.Vec)))
    SLI.WholeError.Mat <- cbind(SLI.WholeError.Mat,SLI.WholeError.Vec)

    SLI.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(LMSquareLossIterations.W.Vec),OZone$BinaryClassification)
    SLI.TrainError.Mat <- cbind(SLI.TrainError.Mat,SLI.TrainError.Vec)

    SLI.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(LMSquareLossIterations.W.Vec),OZone$BinaryClassification)
   SLI.TestError.Mat<- cbind(SLI.TestError.Mat,SLI.TestError.Vec)
    #------------------------------------------------------------------------

    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    ES_CV_Error.fold.n  <- 4
    ES_CV_Error.fold.vec<-Random_Folds(NROW(trainData),ES_CV_Error.fold.n)
    Scalar.Step = 0.1
    Iterations  = 30
    #ES_CV_Error.W.Vec <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],OZone$Folds.Vec,OZone$Folds.n,OZone$Iterations)
    ES_CV_Error.List <- LMSquareLossEarlyStoppingCV(trainData[,1:NCOL(trainData)-1], trainData[,NCOL(trainData)],ES_CV_Error.fold.vec,ES_CV_Error.fold.n,Iterations)
    
    ES_CV_Error.WholeError.Vec   <-Find_Wmatrix_MeanL2Error(OZone$TrainingData, OZone$TrainingLabels,as.matrix(ES_CV_Error.List$w.mat),OZone$BinaryClassification)
    #print("dim ES_CV_Error.WholeError.Vec")
    #print(dim(as.matrix(ES_CV_Error.WholeError.Vec)))
    #ES_CV_Error.WholeError.Mat <- cbind(ES_CV_Error.WholeError.Mat,ES_CV_Error.WholeError.Vec)

    ES_CV_Error.TrainError.Vec <-Find_Wmatrix_MeanL2Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],as.matrix(ES_CV_Error.List$w.mat),OZone$BinaryClassification)
    #ES_CV_Error.TrainError.Mat <- cbind(ES_CV_Error.TrainError.Mat,ES_CV_Error.TrainError.Vec)

    ES_CV_Error.TestError.Vec  <-Find_Wmatrix_MeanL2Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],as.matrix(ES_CV_Error.List$w.mat),OZone$BinaryClassification)
    #ES_CV_Error.TestError.Mat  <- cbind(ES_CV_Error.TestError.Mat,ES_CV_Error.TestError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    Normalized_TrainingData_List <- NormalizeMatrix_List(trainData[,1:NCOL(trainData)-1])
    Penalty.Scalar = 1
    opt.thresh = .2

    SL_L2.W.Matrix <-LMSquareLossL2(Normalized_TrainingData_List$NormalizedMatrix, trainData[,NCOL(trainData)], Penalty.Scalar, opt.thresh,OZone$Initial.Vector)
    DeNormalized.W.Matrix <-(t(SL_L2.W.Matrix))/Normalized_TrainingData_List$sd

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(OZone$TrainingData, OZone$TrainingLabels,t(DeNormalized.W.Matrix),OZone$BinaryClassification)
    SL_L2.WholeError.Vec <-Find_Wmatrix_MeanL1Error(OZone$TrainingData, OZone$TrainingLabels,t(DeNormalized.W.Matrix),OZone$BinaryClassification)
    SL_L2.WholeError.Mat <- rbind(SL_L2.WholeError.Mat,SL_L2.WholeError.Vec)
    
    SL_L2.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(DeNormalized.W.Matrix),OZone$BinaryClassification)
    SL_L2.TestError.Mat <- rbind(SL_L2.TestError.Mat,SL_L2.TestError.Vec)
    
    SL_L2.TrainError.Vec <-Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(DeNormalized.W.Matrix),OZone$BinaryClassification)
    SL_L2.TrainError.Mat <- rbind(SL_L2.TrainError.Mat,SL_L2.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    Penalty.Scalar = 1
    opt.thresh = .2
    SL_L2_Pen.W.Mat <-LMSquareLossL2penalties(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)], OZone$Penalty.Vector)

    #DeNorm.Error <-Find_Wmatrix_MeanL2Error(OZone$TrainingData, OZone$TrainingLabels,t(DeNormalized.W.Matrix),OZone$BinaryClassification)
    print("SL_L2_Pen.WholeError.Vec")
    SL_L2_Pen.WholeError.Vec <-Find_Wmatrix_MeanL1Error(OZone$TrainingData, OZone$TrainingLabels,(SL_L2_Pen.W.Mat),OZone$BinaryClassification)
    SL_L2_Pen.WholeError.Mat <- rbind(SL_L2_Pen.WholeError.Mat,SL_L2_Pen.WholeError.Vec)
    
    print("SL_L2_Pen.TestError.Vec")
    SL_L2_Pen.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],(SL_L2_Pen.W.Mat),OZone$BinaryClassification)
    SL_L2_Pen.TestError.Mat <- rbind(SL_L2_Pen.TestError.Mat,SL_L2_Pen.TestError.Vec)
    
    print("SL_L2_Pen.TrainError.Vec")
    SL_L2_Pen.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],(SL_L2_Pen.W.Mat),OZone$BinaryClassification)
    SL_L2_Pen.TrainError.Mat <- rbind(SL_L2_Pen.TrainError.Mat,SL_L2_Pen.TrainError.Vec)
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
      SL_L2CV.fold.n  <- 4
      SL_L2CV.fold.vec<-Random_Folds(NROW(trainData),SL_L2CV.fold.n)
      
      SL_L2CV.List <- LMSquareLossL2CV(as.matrix(trainData[,1:NCOL(trainData)-1]), as.matrix(trainData[,NCOL(trainData)]),as.matrix(t(SL_L2CV.fold.vec)), as.matrix(OZone$Penalty.Vector))
      

      SL_L2CV.WholeError.Vec <- Find_Wmatrix_MeanL1Error(OZone$TrainingData, OZone$TrainingLabels,(SL_L2CV.List$weight.vec),OZone$BinaryClassification)
      SL_L2CV.WholeError.Mat <- rbind(SL_L2CV.WholeError.Mat,SL_L2CV.WholeError.Vec)
      
      
      #SL_L2CV.TestError.Vec <-Find_Wmatrix_MeanL1Error(trainData[,1:NCOL(trainData)-1],trainData[,NCOL(trainData)],t(SL_L2CV.W.Mat),OZone$BinaryClassification)
      SL_L2CV.TestError.Vec <- SL_L2CV.List$mean.validation.loss
      SL_L2CV.TestError.Mat <- rbind(SL_L2CV.TestError.Mat,SL_L2CV.TestError.Vec)
      print("SL_L2CV.TestError.Vec")
      print(dim(as.matrix(SL_L2CV.TestError.Vec)))
      
      #SL_L2CV.TrainError.Vec <- Find_Wmatrix_MeanL1Error(testData[,1:NCOL(testData)-1],testData[,NCOL(testData)],t(SL_L2CV.W.Mat),OZone$BinaryClassification)
      SL_L2CV.TrainError.Vec <- SL_L2CV.List$mean.train.loss.vec
      SL_L2CV.TrainError.Mat <- rbind(SL_L2CV.TrainError.Mat,SL_L2CV.TrainError.Vec)
      print("SL_L2CV.TrainError.Vec")
      print(dim(as.matrix(SL_L2CV.TrainError.Vec)))
    #------------------------------------------------------------------------
  }

  #------------------------------------------------------------------------
```

### Matrix of loss values
### Train/validation loss plot
```{r}
  #-------------------- Data set 5: Ozone -----------------------------
    #-------------------------LMSquareLossIterations (SLI_Error)--------------
    plot(rowMeans(as.matrix(SLI.TrainError.Mat)),type="o", col = "blue", xlab = "Iterations", ylab = "Error",main = "SAheart Loss of each matrix",ylim=c(1900 ,5000))
    lines(rowMeans(as.matrix(SLI.TestError.Mat)),type="o", col = "light blue")
    #------------------------------------------------------------------------
    
    #--------------------LMSquareLossEarlyStoppingCV (ES_CV_Error)-----------
    lines(rowMeans(as.matrix(ES_CV_Error.TestError.Vec)),type="o", col = "green")
    lines(rowMeans(as.matrix(ES_CV_Error.TrainError.Vec)),type="o", col = "Light green")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2--(SL_L2_Error)------------------
    lines(as.matrix((SL_L2.TestError.Mat[2:NROW(SL_L2.TestError.Mat)])),type="o", col = "black")
    lines(as.matrix(SL_L2.TrainError.Mat[2:NROW(SL_L2.TrainError.Mat)]),type="o", col = "gray")
    #------------------------------------------------------------------------
    
    #-----------------------LMSquareLossL2penalties--(SL_L2_Pen)-------------
    lines(as.matrix((SL_L2_Pen.TestError.Mat[2:NROW(SL_L2_Pen.TestError.Mat)])),type="o", col = "red")
    lines(as.matrix((SL_L2_Pen.TrainError.Mat[2:NROW(SL_L2_Pen.TrainError.Mat)])),type="o", col = "pink")
    #------------------------------------------------------------------------
    
    #-------------------------LMSquareLossL2CV_List-(SL_L2CV)----------------
    lines(as.matrix((SL_L2CV.TestError.Mat[2:NROW(SL_L2CV.TestError.Mat)])),type="o", col = "orange")
    lines(as.matrix((SL_L2CV.TrainError.Mat[2:NROW(SL_L2CV.TrainError.Mat)])),type="o", col = "gold")
    #------------------------------------------------------------------------
  #------------------------------------------------------------------------
```

### Extra Credit attempt: compaire The LinearModels to the KNN
```{r}
  #--------------------NN1ToKmaxPredict------------------------------------
  Ozone<-Prep_Ozone()
  print("NN1ToKmax_Ozone_Tests: ")
  Fold.vec = Random_Folds(Ozone$n_Elements,4)
  Fold.n   = 4
  KNNLearnCV.List = KNNLearnCV(Ozone$TrainingData, Ozone$TrainingLabels, 30, Fold.vec, Fold.n)

  barplot(KNNLearnCV.List$TestMeanError.Means,main = "Ozone: KNNLearnCV L2 Mean Error",xlab = "KNN Compared",ylab = "Error",beside = TRUE)
  #------------------------------------------------------------------------
```

